---
title: "Twitter US Airline Sentiment"
author: "Neha Parulekar"
output: word_document
---
## Additional packages needed
 * If necessary install these packages.

`install.packages("ggplot2");` 
`install.packages("gridExtra");`
`install.packages("maps");`
  
```{r}
require(ggplot2)
require(gridExtra)
require(maps)
```

#loading the data 
```{r}
getwd()
setwd("C:/Users/Neha/Desktop")
data = read.csv('Tweets.csv')
dim(data)
str(data)
```

# Exploratory data analysis: chiecking the columns containing no data (NAs)
```{r}
# find the cells cintaining "" , " " or NAs
data <- as.data.frame(apply(data, 2, function(x) gsub("^$|^$", NA, x)))

# Checking for cols containing NAs and their total number
checkdata <- apply(data, 2, function(x) sum(is.na(x)))
as.data.frame(checkdata )
```
We can see that columns like airline_sentiment_gold and negativereason_gold are mostly empty columns with NAs and have no information. Columns like negativereason, tweet_location and user_timezone has partial data.

I would try to explore Negative sentiment and tweet location.

# Sentiment Analysis:
# trying to get the proportion of tweets with each sentiment

```{r}
prop.table(table(data$airline_sentiment))
```
We can see that most of the tweets contain negative sentiment, as given by the curators of the dataset.

```{r}
# generate a dataframe for plotting in ggplot2 
SmallData <- as.data.frame(prop.table(table(data$airline_sentiment)))
colnames(SmallData) <- c('Sentiment', 'Frequency')
SmallData

# create blank theme for pie chart 


gbar <- ggplot(SmallData, aes(x = Sentiment, y = Frequency, fill = Sentiment))+  scale_fill_brewer(palette="Set3")
gpie = ggplot(SmallData, aes(x = "", y = Frequency, fill = Sentiment)) + scale_fill_brewer(palette="Set3")

plot1 <- gbar + geom_bar(stat = 'identity') + ggtitle("Overall Sentiment") + theme(plot.title = element_text(size = 14, face = 'bold', vjust = 1), axis.title.y = element_text(vjust = 2), axis.title.x = element_text(vjust = -1))

plot2 <- gpie + geom_bar(stat = 'identity') + coord_polar("y", start = 0)  + theme(axis.title.x = element_blank()) + geom_text(aes(y = Frequency/3 + c(0, cumsum(Frequency)[-length(Frequency)]),label = round(Frequency,2)), size = 4) + ggtitle('Overall Sentiment')

grid.arrange(plot1, plot2, ncol = 1, nrow = 2)

```

# Percentage of tweets per airline

```{r}
# get the proportion of tweets per airline and convert it into a dataframe
TweetDataFrame <- as.data.frame(prop.table(table(data$airline)))
colnames(TweetDataFrame) <- c('airline' , 'Frequency')
TweetDataFrame

# Plotting a bar graph to get the percentage of tweets per Airline

gbar <- ggplot(TweetDataFrame, aes(x = airline, y = Frequency, fill = airline))

gbar + geom_bar(stat = 'identity') + scale_colour_gradientn(colours=rainbow(4)) + ggtitle('Percentage of Tweets Per Airline') + theme(plot.title = element_text(size = 14, face = 'bold', vjust = 1)) 
```

# Proportion of Negative sentiments per airline

```{r}
# get the proportion of tweets per airline and convert it into a dataframe

TweetDataFrame <- as.data.frame(prop.table(table(data$airline_sentiment, data$airline )))
colnames(TweetDataFrame) <- c('Sentiment', 'Airline', 'Percentage_Tweets')

# PLotting the graph 

gbar <- ggplot(TweetDataFrame, aes(x = Airline, y = Percentage_Tweets, fill = Sentiment))

# Plotting the graph to show tweet sentiment per 

plot <- gbar + geom_bar(stat = 'identity') +   ggtitle('Proportion of Tweets per Airline') + scale_fill_brewer() + theme (plot.title = element_text(size = 14, face = 'bold', vjust = 1))

plot2 <- gbar + geom_bar(stat = 'identity', position = 'fill') +   ggtitle('Proportion of Tweets per Airline') + scale_fill_brewer() + theme (plot.title = element_text(size = 14, face = 'bold', vjust = 1))

grid.arrange(plot, plot2)

```


# Finding the general Reasons for Negative Sentiment

```{r}
# Creating a data frame to get the reasons for negative tweets

TweetDataFrame <- as.data.frame(prop.table(table(data$negativereason)))
colnames(TweetDataFrame) <- c("reason", "Frequency")
TweetDataFrame
# Removing the first row
TweetDataFrame = TweetDataFrame[-1,]
TweetDataFrame

NegReaplot <- ggplot(TweetDataFrame, aes(x = reason, y = Frequency)) + geom_bar(stat = 'identity', fill = 7) + ggtitle('Reasons for Negative Sentiment') + theme(plot.title = element_text(size = 14, face = 'bold', vjust = 1), axis.title.x = element_text(vjust = -0.1), axis.text.x = element_text(angle = 45, size = 10, vjust = 1))
NegReaplot
```

# Reasons For Negative Sentiment per airline 

```{r}
# First subset the data airline wise then plot to show the reason for negative sentiment

# Subset the data for American Airlines
AmericanAirline <- subset(data, airline = 'American')

# Get the plot
AAplot <- ggplot(as.data.frame(prop.table(table(AmericanAirline$negativereason))), aes(x = Var1, y = Freq)) + geom_bar(stat = 'identity', fill = 'Purple') + ggtitle('American Airlines: Reasons for Negative Sentiment') + theme(plot.title = element_text(size = 14, face = 'bold', vjust = 1), axis.title.x = element_blank(), axis.text.x = element_text(angle = 30, size = 10, vjust = 1))

# Subset the data for US Airways
USAirways <- subset(data, airline = 'US Airways')

# Generate the plot
USAplot <- ggplot(as.data.frame(prop.table(table(USAirways$negativereason))), aes(x = Var1, y = Freq)) + geom_bar(stat = 'identity', fill = 'Purple') + ggtitle('US Airways: Reasons for Negative Sentiment') + theme(plot.title = element_text(size = 14, face = 'bold', vjust = 1), axis.title.x = element_blank(), axis.text.x = element_text(angle = 30, size = 10, vjust = 1))
USAplot

# Subset the data for Delta 
Delta <- subset(data, airline = 'Delta')

# Generate the plot 
Delplot <- ggplot(as.data.frame(prop.table(table(Delta$negativereason))), aes(x = Var1, y = Freq)) + geom_bar(stat = 'identity', fill = 'Purple') + ggtitle('Delta : Reasons for Negative Sentiment') + theme(plot.title = element_text(size = 14, face = 'bold', vjust = 1), axis.title.x = element_blank(), axis.text.x = element_text(angle = 30, size = 10, vjust = 1))
Delplot

# Subset the data for Southwest 
Southwest <- subset(data, airline = 'Southwest')

# Generate the plot 
SWplot <- ggplot(as.data.frame(prop.table(table(Southwest$negativereason))), aes(x = Var1, y = Freq)) + geom_bar(stat = 'identity', fill = 'Purple') + ggtitle('Southwest : Reasons for Negative Sentiment') + theme(plot.title = element_text(size = 14, face = 'bold', vjust = 1), axis.title.x = element_blank(), axis.text.x = element_text(angle = 30, size = 10, vjust = 1))
SWplot

# Subset the data for Virgin 
Virgin <- subset(data, airline = 'Virgin')

# Generate the plot 
Virplot <- ggplot(as.data.frame(prop.table(table(Virgin$negativereason))), aes(x = Var1, y = Freq)) + geom_bar(stat = 'identity', fill = 'Purple') + ggtitle('Virgin : Reasons for Negative Sentiment') + theme(plot.title = element_text(size = 14, face = 'bold', vjust = 1), axis.title.x = element_blank(), axis.text.x = element_text(angle = 30, size = 10, vjust = 1))
Virplot


# Subset the data for United
United <- subset(data, airline = 'United')

# Generate the plot 
Unplot <- ggplot(as.data.frame(prop.table(table(United$negativereason))), aes(x = Var1, y = Freq)) + geom_bar(stat = 'identity', fill = 'Purple') + ggtitle('United : Reasons for Negative Sentiment') + theme(plot.title = element_text(size = 14, face = 'bold', vjust = 1), axis.title.x = element_blank(), axis.text.x = element_text(angle = 30, size = 10, vjust = 1))
Unplot

```

# Location of tweets: Visualisation on maps
```{r}
# Get locations of the tweet
Location <- data$tweet_coord
Location <- Location[complete.cases(Location)]
Location <- as.data.frame(Location)
Location$count = 1 
Location$Location = as.character(Location$Location)

# remove the duplicate coordinates and count the no of time they appear
Location <- aggregate(count ~ Location, data = Location, FUN = sum)
Location <- Location[-5]
coords <- strsplit(Location$Location,",")

# Now separate longitude and latitude

lat <- NULL
long <- NULL

for (i in 1:length(coords)) {
  
  lat = c(lat, substring(coords[[i]][1], 2))
  long = c(long, coords[[i]][2])
}

Location$lat = lat
Location$long = long 

Location$long = substr(Location$long, 1, nchar(Location$long)-1)

head(Location)
dim(Location)

# PLot these on the map of United States

UStates <- map_data("state")
UStates$group <- as.factor(UStates$group)

USplot <- ggplot() 

USplot + geom_polygon(data=UStates, aes(x=long, y=lat, group = group), fill = 'lightblue') + ggtitle("Location of tweets across the United States")

USplot +  geom_point(data=Location, aes(x=long, y=lat, size = count), color = "coral1") + scale_size(name="Total Tweets")

USplot + xlim(-125, -65) + ylim(25, 50)

USplot
```
