---
title: "Module8L2"
author: "Neha Parulekar"
date: "April 8, 2016"
output: word_document
---

# Additional packages needed
* If necessary install the followings packages.

`install.packages("splitstackshape");`   
`install.packages("tm");`   
`install.packages("stringr");` 
`install.packages("wordcloud");`
`install.packages("plyr");`

```{r}
library(tm)
library(splitstackshape)
library(stringr)
library(wordcloud)
library(plyr)
```


# Assingment

Create regular expressions for the patterns below: 

***Match any of the following punctuation characters in the ASCII table:  !"#$%&'()+,**

```{r}
ascii<-c("$","!","}","#","^","*","&")
grep("[\\!|\"|\\#|\\$|\\%|\\&|\\'|\\(|\\)|\\+|\\,]",ascii)
```

***Create one regular expression to match all common misspellings of calendar**

```{r}
commonMisSpellings<-c("calendar","calender","calandar","calander","colander")
grep("c[a|o]l[e|a]nd[a|e]r",commonMisSpellings)
```

***Create one regular expression to match any character except line breaks.**
```{r}
Quote <- c("You have brains in your head.",
          " You have feet in your shoes.")
grep("([\\w\\s\\d[:punct:]])\n",Quote)

```

***You need to validate a ZIP code (U.S. postal code), allowing both the five-digit and nine-digit (called ZIP+4) formats. The regex should match 02115 and 02115-5515, but not 2115, 2115-5515, 21155515,021155515, etc.**

```{r}
validateZipcode<- function(zip){
  if(length(grep("^\\d{5}([\\-]\\d{4})?$",zip))==0){
    print("Invalid zip")
  }else{
    print("Valid zip")
  }
  }
validateZipcode("02215-2113")
validateZipcode("022152113")
```

***You need to validate a legit any password for your website. Passwords have the following complexity requirements: Length between 8 and 32 characters, ASCII visible and space characters only, One or more uppercase letters, One or more lowercase letters, One or more special characters (ASCII punctuation)** 

```{r}
validatePassword <- function(passwd){
  if(nchar(passwd)>=8 & nchar(passwd)<=32){
    if(length(grep("[^\\x00\\x08\\x0B\\x0C\\x0E-\\x1F]*",passwd))==0){
      print("Invalid password: password can only have printable characters")
    }else if(length(grep("[A-Z]",passwd))==0){
      print("Invalid password: Atleast 1 uppercase letter is required")
    }else if(length(grep("[a-z]",passwd))==0){
      print("Invalid password: Atleast 1 lowercase letter is required")
    }else if(length(grep("[[:punct:]]",passwd))==0){
      print("Invalid password: Atleast 1 special character is required")
    }else{
      print("This is a Valid password")
    }
  }else{
    print("Incorrect password: make sure that you password is more than 8 characters and less than 32.")
  }
}

validatePassword("zap")
validatePassword("computer")
validatePassword("Computer")
validatePassword("COMPUTER")
validatePassword("C@mputer")
```

***Load the file M08_tweets.csv (it is online at  'http://nikbearbrown.com/YouTube/MachineLearning/M08/M08_tweets.csv')**

```{r}
data_url <- 'http://nikbearbrown.com/YouTube/MachineLearning/M08/M08_tweets.csv'
twitter <- read.csv(url(data_url),stringsAsFactors=F)
colnames(twitter)<-"X"
```

***Do the following:**
**Extract a list of the top 9 users (e.g. @NikBearBrown)**
```{r}
twi<-cSplit(twitter, "X", " ")
names<-sapply(1:34, function(i) (text=paste0("X_",i))) 
setnames(twi,colnames(twi),names)

t<-grep("^\\@",sapply(1:34, function(i) eval(parse(text=paste0("twi$X_",i)))),value=T)

head(sort(table(t),decreasing=T),9)
```

Extract a list of the top 9 hashtags (e.g. #Bear)

```{r}
t<-grep("^\\#",sapply(1:34, function(i) eval(parse(text=paste0("twi$X_",i)))),value=T)

head(sort(table(t),decreasing=T),9)
```

Find the top 5 most positve tweets and Negative tweets
```{r}
#Load data
data_url <- 'http://nikbearbrown.com/YouTube/MachineLearning/M08/M08_tweets.csv'
twitter <- read.csv(url(data_url),stringsAsFactors=F)
# reduce the data
Twitter <- twitter[1:500,]

# Positive tweets 
PosTweet <- grep("great", Twitter)
Twitter[PosTweet]

# Negative tweets
NegTweet <- grep("fuck", Twitter)
Twitter[NegTweet]
```

Create a world cloud of 100 related tweets
```{r}

#Twitter_hash <- str_extract_all(Twitter, "@\\w+")
#Tweetdata <- Twitter_hash

Tweetdata.clean <- Corpus(VectorSource(Twitter))
Tweetdata.clean <- tm_map(Tweetdata.clean, stripWhitespace)
Tweetdata.clean<-  tm_map(Tweetdata.clean, content_transformer(tolower))
Tweetdata.clean<- tm_map(Tweetdata.clean, removePunctuation)
Tweetdata.clean <- tm_map(Tweetdata.clean, removeWords, stopwords("english"))
inspect(Tweetdata.clean)

# Document Term Matrix

dtm <- DocumentTermMatrix(Tweetdata.clean)
dtm2 <- as.matrix(dtm)
frequency <- colSums(dtm2)
frequency <- sort(frequency, decreasing=TRUE)
V <- sort(rowSums(dtm2), decreasing = TRUE)
myNames <- names(V)
data <- data.frame(word = myNames, freq = V)
wordcloud(data$word, data$freq, min.freq=5)
words<-names(frequency)
wordcloud(words[1:100], frequency[1:100], colors=brewer.pal(8, "Dark2"))

```

***Which tweets could be classified as game development?**

```{r}
gamedev<-(grep("\\#gamedev",twitter$X,value=T))
head(gamedev)
```