---
title: "Module 1"
author: "Neha Parulekar"
date: "January 25, 2016"
output: word_document
---

## M1L2 Homework

This homework assignment focuses on Probability Distributions. 

* Replicate and plot the fat-tailed Cauchy distributions from https://en.wikipedia.org/wiki/Cauchy_distribution

To run the code in you may need additional packages.

If necessary install `ggplot2` package.

`install.packages("ggplot2"); 

```{r}
require(ggplot2)
```

```{r}
 trails <- 3333
 Rcauchy <- data.frame(A=rcauchy(n=trails, location=0, scale=0.5),
B=rcauchy(n=trails, location=0, scale=1),  C=rcauchy(n=trails, location=0, scale=2), D=rcauchy(n=trails, location=-2, scale =1))
 
head(Rcauchy)
summary(Rcauchy)

library(reshape)
rnd <- melt(data=Rcauchy)

## No id variables; using all as measure variables

head(rnd)

library(ggplot2)
ggplot(rnd, aes(x=value)) + geom_density(aes(group=variable,color=variable)) + labs(title="Wikipedia Cauchy Distributions", y="P(X)", x="X") + xlim(-5,5)

    ```
    
* Load the file M01_Lesson_02_Q1.csv
* Answer the following questions for the data in each column:
    * How is the data distributed?
    * What are the summary statistics?
    * Are there anomalies/outliers?
    * Try to regenerate the data in each column.
    * Plot your regenerated data versus the original data using a faceted graph. How does it compare? 
    
```{r}
setwd("C:/Users/Neha/Desktop")
dataset <- read.csv("M01_Lesson_02_Q1.csv")
head(dataset)
    ```
    
**Answers**

1. How is the data distributed?

Distribution of a single variable can be showed by density plots and histograms.

**A**

```{r}
qplot(A, data = dataset, geom = "histogram")
qqnorm(dataset$A)
qqline(dataset$A)
```

*From the plots above we can say that the data is normally distributed*

2. What are the summary statistics?

```{r}
summary(dataset$A)
```

3. Are there anomalies/outliers?
* There are outliers at 4 and between 13-14


**B**

```{r}
qplot(B, data = dataset, geom = "histogram")
qqnorm(dataset$B)
qqline(dataset$B)
```

*From the plots above we can say that the data is normally distributed*

2. What are the summary statistics?

```{r}
summary(dataset$B)
```

3. Are there anomalies/outliers?
* There are outliers at -3 and beyond 2

**C**


```{r}
qplot(C, data = dataset, geom = "histogram")
qqnorm(dataset$C)
qqline(dataset$C)
ggplot(dataset)+aes(x=C) + geom_density()
```

*From the plots above we can say that the data is distributed binomially from right skew and integer values*

2. What are the summary statistics?

```{r}
summary(dataset$C)
```

3. Are there anomalies/outliers?
* There are no outliers.


**D**

```{r}
qplot(D, data = dataset, geom = "histogram")
qqnorm(dataset$D)
qqline(dataset$D)
ggplot(dataset)+aes(x=D) + geom_density()
```

*From the plots above we can say that the data is distributed binomially from right skew and integer values*

2. What are the summary statistics?

```{r}
summary(dataset$D)
```

3. Are there anomalies/outliers?
* There are no outliers.

**E**

```{r}
qplot(E, data = dataset, geom = "histogram")
qqnorm(dataset$E)
qqline(dataset$E)
```

* From the plots above we can say that the data is distributed uniformaly*

2. What are the summary statistics?

```{r}
summary(dataset$E)
```

3. Are there anomalies/outliers?
* There are no outliers.


* Try to regenerate the data in each column.

```{r}
set.seed(100)
trails <- 333
RA <- rnorm(n=trails, mean=9.079, sd=2.89)
RB <- rnorm(n=trails, mean=0.030, sd=1.29)
RC <- rbinom(n=trails, size=9, p=0.7)
RD <- rbinom(n=trails, size=18,p=0.11)
min<-33.52
max<-331.80
RE <- runif(trails, min, max+1)
regdata<- data.frame(RA,RB,RC,RD,RE)
summary(regdata)
```

* Plot your regenerated data versus the original data using a faceted graph. How does it compare? 

```{r}
pairs(dataset[,2:6])
pairs(regdata[,1:5])

