---
title: "Module4L4"
author: "Neha Parulekar"
date: "February 28, 2016"
output: word_document
---

## Additional packages needed
 
To run the code in M04_Lesson_04.Rmd you may need additional packages.

* If necessary install these packages.

`install.packages("arules");`    
`install.packages("arulesViz");`       
`install.packages("Matrix");`    
      

```{r}
require(arules)
require(arulesViz)
require(Matrix)
```

**Loading the data** I choose chess data from the link given.

```{r}
# Checking the working directory and loading the data
setwd("c:/Users/Neha/Desktop")
ChessData <- read.table(file = "chess.dat" ,sep=",")
head(ChessData)
summary(ChessData)

# # default settings result in zero rules learned
ChessData.d <- apriori(ChessData, parameter = list(support = 0.1, confidence = 0.8, minlen = 1))
summary(ChessData.d)

# set better support and confidence levels to learn more rules

# Tried different sets of rules but still get the output value as 0.
ChessData.d <- apriori(ChessData, parameter = list(support = 0.02, confidence = 0.9, minlen = 2))
summary(ChessData.d)

ChessData.d <- apriori(ChessData, parameter = list(support = 0.01, confidence = 0.5, minlen = 4))
summary(ChessData.d)

ChessData.d <- apriori(ChessData, parameter = list(support = 0.05, confidence = 0.5, minlen = 1))
summary(ChessData.d)

```


##**Association Rules with Apriori Algorithms**
Assoiation rules with Apriori Algorithms is generally used for mining frequent itemsets.The Apriori algorithm employs level-wise search for frequent itemsets. The implementation of Apriori used includes some improvements (e.g., a prefix tree and item sorting).

###**Usage**
apriori(data, parameter = NULL, appearance = NULL, control = NULL)

### Arguments

**Data**  any data structure which can be coerced into transactions (e.g., a binary matrix or data.frame).

**Parameter** object of class APparameter or named list. The default behavior is to mine rules with support 0.1, confidence 0.8, and maxlen 10.

**Appearance** object of class APappearance or named list. With this argument item appearance can be restricted (implements rule templates). By default all items can appear unrestricted.

**Control** object of class APcontrol or named list. Controls the algorithmic performance of the mining algorithm (item sorting, etc.)

###**Values**
Returns an object of class rules or itemsets.


#### Reference : http://www.inside-r.org/packages/cran/arules/docs/apriori
