---
title: "Module 3"
author: "Neha Parulekar"
date: "February 8, 2016"
output: word_document
---

## Additional packages needed
 
To run the code in M03_Lesson_02.Rmd you may need additional packages.

* If necessary install the following packages.

* `install.packages("ggplot2");`   
* `install.packages("reshape2"); `  
* `install.packages("psych");`    


```{r}
require(ggplot2)
require(reshape2)
require(psych)

```

## Assignment 

* Download the compressed data from the U.S. [Bureau of Labor Statistics](https://en.wikipedia.org/wiki/Bureau_of_Labor_Statistics
) [http://www.bls.gov/](http://www.bls.gov/) @ http://www.bls.gov/cew/data/files/2014/csv/2014_annual_singlefile.zip, and extract the .csv file.  
* Run Principal Components Analysis on the BLS data and answer the following questions. (You can use any PCA function you wish, i.e. princomp(), prcomp(),  principal() or by hand.)    
**Reading the file**

```{r}
# set the working directory
setwd( "C:/Users/Neha/Desktop")
# loading the data
LaborStatistics <- read.csv("2014.annual.singlefile.csv")

# Checking the data 
names(LaborStatistics)

# retriving the dimensions of the data
dim(LaborStatistics)

# Removing the first eight columns from the data 
RemoveCols <- c("area_fips","industry_code","size_code","qtr","own_code","agglvl_code","year","disclosure_code","lq_disclosure_code","oty_disclosure_code")
LaborStatistics <- LaborStatistics[,!(names(LaborStatistics) %in% RemoveCols)]

# checking the dimensions of the data
dim(LaborStatistics)
```


* **Run Principal Components Analysis on the BLS data and answer the following questions. (You can use any PCA function you wish, i.e. princomp(), prcomp(),  principal() or by hand.)**


```{r}
LaborStatistic.fit.A <-  princomp(formula = ~., data = LaborStatistics, cor = TRUE, na.action=na.exclude)
print(LaborStatistic.fit.A)
LaborStatistic.fit.B <- prcomp(LaborStatistics,center = TRUE, scale.= TRUE)
#print(LaborStatistic.fit.B)

# getting the summary
summary(LaborStatistic.fit.A)
names(LaborStatistic.fit.A)
summary(LaborStatistic.fit.B)
```

* **Barplot**
```{r}
#plotting the screeplot, barplot, biplot
#screeplot(LaborStatistic.fit.A)
barplot(LaborStatistic.fit.A$sdev/LaborStatistic.fit.A$sdev[1])
#biplot(LaborStatistic.fit.A, expand=100, xlim=c(-0.1, 0.1), ylim=c(-0.1, 0.1)) 
```

* **ggbiplot**
```{r}
#loadint the required package and plotting ggbiplot

library(devtools)
install_github("vqv/ggbiplot")
library(ggbiplot)
fit<- princomp(LaborStatistics, cor=TRUE)
ggbiplot(fit, labels = rownames(LaborStatistics))

```

## **Answers**

**(a) What proportion of the total variation in the data is explained by each of the principal  components?**

* PC1    PC2    PC3    PC4     PC5     PC6    PC7  
*  0.3404 0.1363 0.1011 0.0865 0.06378 0.04998 0.0483

* PC8     PC9    PC10    PC11    PC12    PC13    
* 0.03864 0.03469 0.03117 0.02279 0.01507 0.00894

* PC14    PC15    PC16    PC17   PC18    PC19
* 0.00576 0.00536 0.00471 0.00331 0.0011 0.00064

* PC20    PC21    PC22    PC23    PC24    PC25
* 0.00057 0.00047 0.00025 0.00008 0.00002 0.000000

* PC26      PC27     PC28
* 0.000000 0.0000000 0.000000
 

**(b) Plot a screeplot.**
```{r}
screeplot(LaborStatistic.fit.A)
```
The screeplot is a decreasing plot which shows variance of the first ten PCs. 

**(c) Based on the variation explained for each of these components, which, if any, components would you use?**
As we can see more than 90% of variance of the data was captured by first 10 PCs. So it would be sufficient to use those components.


**(d) Is there evidence of clustering in the data by creating biplots of the each of the components plotted against one another?**
*It takes too long to run.* 
But running the **ggbiplot** we can see that there is clustering in data.


**(e) Do any of the biplots reveal any interesting structure?**
*The biplot takes too long to run*
Ruuning **ggbiplot** we can see the points in the labor statistics data would fall when we project from 28 space to 2 space.They are not evenly scattered about the projections.

**(f) How many pcs are required to explain 75% of the variance in the data?**
Seven PCs are required to explain 75% of the variance in the data.

