---
title: "Module1L3"
author: "Neha Parulekar"
date: "January 25, 2016"
output: word_document
---

## Homework Question 2

_Exploratory Data Analysis assignment_

* Load the file M01_quasi_twitter.csv
* Answer the following questions for the data in each column:
    * How is the data distributed?
    * Test distribution assumptions (e.g. normal distributions or skewed?)
    * What are the summary statistics?
    * Are there anomalies/outliers?
* identify useful raw data & transforms (e.g. log(x))
* identify data quality problems
* identify outliers
* identify subsets of interest
* suggest functional relationships

To run the code in you may need additional packages.

If necessary install `ggplot2` package.

`install.packages("ggplot2"); 

```{r}
require(ggplot2)
```


```{r}
setwd("C:/Users/Neha/Desktop")
twitterdataset <-read.csv("M01_quasi_twitter.csv")
head(twitterdataset)
library(ggplot2)
qplot(screen_name, data=twitterdataset) 
```

**Answers**

1. The data is distributed normally.
2. The data follows uniform distribution, thus no normal or skewed distribution.

3. The summary of the data set is
```{r}
summary(twitterdataset$screen_name)
```
4. There are no outliers.
5. There are no transforms, quality problems, outliers, subset intrest.


**created_at_month**
```{r}
qplot(created_at_month, data=twitterdataset)
qqnorm(twitterdataset$created_at_month)
qqline(twitterdataset$created_at_month)
```

1. skewed distribution to the left
2. this is not a normal distribution
3. summary
```{r}
summary(twitterdataset$created_at_month)
```
4. No
5. No

**created_at_day**
```{r}
ggplot(twitterdataset)+aes(x=created_at_day)+geom_histogram()
```

1. uniform distribution 
2. this is not a normal distribution
3. summary
```{r}
summary(twitterdataset$created_at_day)
```
4. drop at no 34
5. no

**created_at_year**
```{r}
ggplot(twitterdataset)+aes(x=created_at_year)+geom_histogram()
```

1.uniform distribution with peaks in 2009 and 2014. 
2. Not a normal distribution.
3. summary
```{r}
summary(twitterdataset$created_at_year)
```
4.outlier at 2006
5. No

**country**
```{r}
qplot(country, data=twitterdataset)
```

1.uniform distribution with peak at USA
2. not a normal distribution
3. summary
```{r}
summary(twitterdataset$country)
```
4. no
5. no

**location**
```{r}
qplot(location, data=twitterdataset)
```

1. its a uniform distribution
2. not a normal distribution
3. sumary
```{r}
summary(twitterdataset$location)
```
4. No
5. No

**friends_count**
```{r}
qplot(friends_count, data=twitterdataset)
qqnorm(twitterdataset$friends_count)
qqline(twitterdataset$friends_count)
```

1. skewed distribution to the left
2. not a normal distribution
3. summary
```{r}
summary(twitterdataset$friends_count)
```
4. No
5. No

**followers_count**
```{r}
qplot(followers_count, data=twitterdataset)
qqnorm(twitterdataset$followers_count)
qqline(twitterdataset$followers_count)
```
1. skewed distribution
2. not a normal distribution
3. summary
```{r}
summary(twitterdataset$followers_count)
```
4. outliers beyond 5million
5. No

**statuses_count**

```{r}
qplot(statuses_count, data=twitterdataset)
qqnorm(twitterdataset$statuses_count)
qqline(twitterdataset$statuses_count)
```
1. skewed distribution
2. not a normal distribution
3. summary
```{r}
summary(twitterdataset$followers_count)
```
4. outliers present
5. No

**favourites_count**

```{r}
qplot(favourites_count, data=twitterdataset)
qqnorm(twitterdataset$favourites_count)
qqline(twitterdataset$favourites_count)
```

1. skewed distribution
2. Not a normal distribution
3. summary
```{r}
summary(twitterdataset$favourites_count)
```
4. outliers present
5. No

**dob_day**
```{r}
ggplot(twitterdataset)+aes(x=dob_day)+geom_histogram()
```
1. uniformly distributed
2. not a normal distribution
3. summary
```{r}
summary(twitterdataset$dob_day)
```
4. outliers at 31
5. No

**dob_year**
```{r}
ggplot(twitterdataset)+aes(x=dob_year)+geom_histogram()
```
1. uniform distribution with a peak at 1990
2. No
3. summary
```{r}
summary(twitterdataset$dob_day)
```
4. no
5.no

**dob_month**
```{r}
qplot(dob_month, data=twitterdataset)
qqnorm(twitterdataset$dob_month)
qqline(twitterdataset$created_at_month)
```
1. uniform distribution
2. no
3. summary
```{r}
summary(twitterdataset$dob_month)
```
4 outliers beyond 1500
5. no

**gender**
```{r}
qplot(gender, data=twitterdataset)
```
1. uniform distribution
2. no
3. summary
```{r}
summary(twitterdataset$gender)
```
4. outliers at 0
5. No

**education**
```{r}
qplot(education, data=twitterdataset)
```
1. No
2. Normal distribution
3. summary
```{r}
summary(twitterdataset$education)
```
4. no
5.no

**experience**
```{r}
qplot(experience, data=twitterdataset)
```
1. uniform distribution
2. No
3. summary
```{r}
summary(twitterdataset$experience)
```
4. outliers present
5. no


6. There can be a functional relationship between the age and the friends count or age and followers count
```{r}
qplot(dob_year, friends_count, data=twitterdataset)
qplot(dob_year, followers_count, data=twitterdataset)
```


